Generative AI for image reconstruction in Intensity Interferometry: a first attempt

### 2025-12-07 Phase_II/draft/ParaGan.tex
to Prof. Saha

\section{Network Parameters}
\begin{figure*}
	\centering
	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_7.png}
	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_12.png}
	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_13.png}
	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_29.png}
	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_39.png}
\caption{Example results of image reconstruction using the cGAN model along with the II observations simulated in this work. Each row in this figure represents the results for a hypothetical fast-rotating star. The left panel represents the sparse II pattern obtained by the simulated observation of the star using the four IACTs illustrated in Fig.\ref{fig:teles}. This image acts as the ``condition'' part of the data input to the cGAN model. The second panel from left displays the real image, or ground truth, which the Discriminator uses to distinguish from the images generated by the Generator. The data generated for training, validation and testing of the cGAN model is a merge of this image and its II pattern presented in the left panel. The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model . The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane.}
	\label{fig:GAN}
\end{figure*}
An appropriate cGAN architecture along with a set of hyperparameters was optimized by tuning. The objective of the model, as already mentioned, was to learn to faithfully reproduce a set of sky-images of fast rotators subject to the condition that those images are consistent with their simulated II observation data. We discuss below the architecture and the hyperparameters of the cGAN model used for this task. Given the adversarial nature of GANs, where the Generator and Discriminator engage in a minimax game, careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.

>>>>

\section{Network Parameters}
\begin{figure*}
	\centering
	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_4.png}
	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_17.png}
	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_22.png}
	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_30.png}
	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_50.png}
	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_75.png}
\caption{Example results of image reconstruction using the cGAN model along with the II observations simulated in this work. Each row in this figure represents the results for a hypothetical fast-rotating star. The left panel represents the sparse II pattern obtained by the simulated observation of the star using the four IACTs illustrated in Fig.\ref{fig:teles}. This image acts as the ``condition'' part of the data input to the cGAN model. The second panel from left displays the real image, or ground truth, which the Discriminator uses to distinguish from the images generated by the Generator. The data generated for training, validation and testing of the cGAN model is a merge of this image and its II pattern presented in the left panel. The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model . The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane.}
	\label{fig:GAN}
\end{figure*}
An appropriate cGAN architecture along with a set of hyperparameters was optimized by tuning. The objective of the model, as already mentioned, was to learn to faithfully reproduce a set of sky-images of fast rotators subject to the condition that those images are consistent with their simulated II observation data. We discuss below the architecture and the hyperparameters of the cGAN model used for this task. Given the adversarial nature of GANs, where the Generator and Discriminator engage in a minimax game, careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.
